Blocking-resistant communication\\through domain fronting

### 2014-07-16 docs/meek.tex
Dust.
Cite TapDance.

The other category of obfuscation contains transports that take the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus}
encodes traffic to look like a cover protocol, such as unencrypted HTTP,
using special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
and sends it over VoIP to a proxy which decodes and forwards it to the destination.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings that match a given regular expression,
in order to match a firewall's whitelist or avoid matching a blacklist.

@@

% Infranet
% Freegate
% Ultrasurf
% Dust

@@

Decoy routing~\cite{decoyrouting} is a technique that puts
proxies in the middle of network paths, rather than at the ends.
Realizations of decoy routing include Telex~\cite{telex}
and Cirripede~\cite{cirripede}.
In decoy routing, friendly ISPs deploy special \emph{decoy} routers that lie
on network paths between censored users and uncensored Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by decoy routers, and not by the censor.
On receiving a tagged communication, the decoy shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar to decoy routing;
think of domain fronting as decoy routing at the application layer.
In place of a decoy router, domain fronting has a CDN edge server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while domain fronting uses the HTTP Host header, encrypted within HTTPS.

>>>>

The other category of obfuscation contains transports that take the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus}
encodes traffic to look like a cover protocol, such as unencrypted HTTP,
using special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
and sends it over VoIP to a proxy which decodes and forwards it to the destination.
Dust~\cite{dust} uses encryption to hide static byte patterns and then
shapes statistical features such as packet length and byte frequency to
match given distributions.
fteproxy~\cite{fte} uses format-transforming encryption to encode data into strings that match a given regular expression,
in order to match a firewall's whitelist or avoid matching a blacklist.

@@

% Infranet
% Freegate
% Ultrasurf

@@

Decoy routing~\cite{decoyrouting}, also called end-to-middle proxying,
is a technique that puts
proxies in the middle of network paths, rather than at the ends.
Realizations of decoy routing include Telex~\cite{telex},
Cirripede~\cite{cirripede}, and TapDance~\cite{tapdance}.
In decoy routing, friendly ISPs deploy special routers that lie
on network paths between censored users and uncensored Internet destinations.
Circumvention traffic is ``tagged'' in a way that is detectable only
by decoy routers, and not by the censor.
On receiving a tagged communication, the decoy shunts it away from its apparent, \emph{overt destination}
and toward a censored, \emph{covert destination}.
Domain fronting is similar to decoy routing;
think of domain fronting as decoy routing at the application layer.
In place of a decoy router, domain fronting has a CDN edge server;
in place of the overt destination is the front domain.
Both systems tag flows in a way that is invisible to the censor:
decoy routing uses, for example, a hash embedded in a client nonce,
while domain fronting uses the HTTP Host header, encrypted within HTTPS.
